### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
succesfully included R results in the manuscript.

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(psych)
library(betareg)
library(lmerTest)
library(forcats)
library(GPArotation)

@@

## Descriptives
The mean sample size within the replications was `r printnum(round(mean(coded_data_replications$N, na.rm = TRUE)))` participants (IQR = `r printnum(round(IQR(coded_data_replications$N, na.rm = TRUE)))`). In the original articles the mean sample size was `r printnum(round(mean(coded_data_original_shortened$N, na.rm = TRUE)))` (IQR = `r printnum(round(IQR(coded_data_original_shortened$N, na.rm = TRUE)))`). In total, support was found for hypothesized effects of `r printnum(table(coded_data_replications$hypothesis_support)["Yes"])` of the `r printnum(nrow(coded_data_replications)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)

@@

## Descriptives

```{r Code for Descriptives Retrieval}
N_replications <- mean(coded_data_replications$N, na.rm = TRUE)
IQR_replications <- IQR(coded_data_replications$N, na.rm = TRUE)
N_original <- mean(coded_data_original_shortened$N, na.rm = TRUE)
IQR_original <- IQR(coded_data_original_shortened$N, na.rm = TRUE)

N_h_support <- table(coded_data_replications$hypothesis_support)["Yes"]
N_measures <- nrow(coded_data_replications)
```

The mean sample size within the replications was `r apa_num(N_replications, digits = 0)` participants (IQR = `r apa_num(IQR_replications, digits = 0)`). In the original articles the mean sample size was `r apa_num(N_original, digits = 0)` (IQR = `r apa_num(IQR_original, digits = 0)`). In total, support was found for hypothesized effects of `r apa_num(N_h_support, digits = 0)` of the `r apa_num(N_measures, digits = 0)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.
